News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-03-24 rupnik2015.tex
discussion and future work

\begin{abstract}
Today, we follow news which is distributed globally. Significant events are reported by different sources and in different languages. In this work, we address the problem of tracking and events in a large multilingual stream. We consider a particular aspect of this problem, namely how to link collections of articles in different languages which refer to the same event. Given a multi-lingual stream and clusters of articles from each language, we first propose a method for cross-lingual document similarity based on Wikipedia, which enables us to compute the similarity of any two articles regardless of language. The proposed method is can scale to 100 languages and can match articles from languages with little or no direct overlap in the training data. Using this similarity, we then propose an approach to link clusters of articles across languages which represent the same event. We provide an extensive evaluation of the system as a whole, as well as an evaluation of the quality and robustness of the similarity measure and the linking algorithm.
\begin{comment}
Main points:
\begin{itemize}
\item Problem of tracking events in a large multilingual stream - we reduce it to event linking
\item Two contributions. We propose a method that enables cross-lingaul document similarity an approach to linking multilingual data and an approach that uses is to link events.
\item Evaluation of cross-lingual approaches on Wikipedia and the event linking task.
\end{itemize}
\end{comment}
\end{abstract}
%\section{Overview}
%Structure
%\begin{itemize}
%\item Introduction
%\item Cross lingual document similarity (model)
%\item  Event Detection
%\item  Combing the approaches
%\item Experiments
%\item Conclusions
%\end{itemize}
%The story:
%\begin{itemize}
%\item Description of the problem - we would liek to understand events ans sequences of events, but our observables (e.g. news stories) occur in a variety of languages
%\item We present an approach to tackle this problem using a combination of techniques....
%\item Ultimately we present a tool showing the feasibility of our approach
%%\end{itemize}
%
%\section{Overview}
%Structure
%\begin{itemize}
%\item Introduction
%\item System overview
%\item Cross lingual document similarity (algorithms)
%\item Event linking
%\item Experiments
%\item Conclusions
%\end{itemize}
%The story:
%\begin{itemize}
%\item Description of the problem - we would like to understand global news as sequences of events, but our observables (e.g. news stories) occur in a variety of languages
%\item We present an approach to tackle this problem using a combination of techniques....
%\item Ultimately we present a tool showing the feasibility of our approach
%\end{itemize}
%

@@

The main application on which we test the above similarity is cross-lingual event linking. In online media streams -- particularly new articles -- there is often duplication of reporting, different viewpoints or opinions, all centering around a single event. Same events are covered by many articles and the question we address is how to find all the articles in different languages that are describing a single event. We base our evaluation on an online system for detection of world events, called Event Registry. We do not address the problem of detection of events in this paper but rather consider the problem that given a series of events, how may we best ``tag" or match articles in different languages to these events. The events are represented by clusters of articles and so ultimately our problem reduces to find suitable matchings between clusters with articles in different languages.

@@

The problem of cross-lingual event linking is to identify the clusters describing the same events. Each article $a_i$ is written in a language $l$, where $\ell \in L = \{\ell_1,\ell_2,...,\ell_k\}$. For each language $\ell$, we generate and maintain a set of language-specific clusters $C_l$. That is, all articles are in language $l$. For any cluster $c_i \in C_{\ell_a}$, we would like to identify clusters $c_j \in C_{\ell_b}$ (where $\ell_a \neq \ell_b$) that describe the same event as $c_i$. We define \emph{equivalent clusters} as  pairs $(c_i,c_j)$ such that both clusters in the pair describe the same event in languages $C_{\ell_a}$ and $C_{\ell_b}$ respectively. Furthermore, we iterate over all the languages we consider. That is, given a cluster in language $\ell_i$, we look for matching clusters in language $\ell_j$ for $i\neq j$  in a pairwise fashion.

@@

Furthermore, the matching of clusters is a \emph{generalized matching}. We cannot assume that there is only one cluster per language per event, nor can we assume complete coverage -- that there exists at least one cluster per event in every language. This implies that we cannot make any assumptions on the matching, e.g. one-to-one, complete, etc. This excludes the use of standard weighted bipartite matching type of algortihms for this problem. An example is shown in Figure~\ref{fig:clusters}, where a cluster may contain articles which are closely matched with many clusters in a different language.

We impose an additional requirement.  Identification of the equivalent clusters cannot be done exhaustively -- for a cluster $c_i$ we wish to avoid testing all other clusters for all the other languages. Performing exhaustive comparison for each cluster $c_i$ would result in $O(N^2)$ tests, where $N$ is the number of all clusters (over all languages), which is not feasible when the number of clusters is on the order of tens of thousands.

@@

Although there are a number of services that aggregate news by identifying clusters of similar articles, there are almost no services that provide linking of clusters over different languages. Google News as well as Yahoo! News are able to identify clusters of articles about same event, but they offer no linking of clusters across languages. The only service that we found, which provides cross-lingual cluster linking, is the European Media Monitor (EMM)~\cite{Steinberger2008}. EMM clusters articles in 60 languages and then tries to determine which clusters of articles in different languages describe the same event. To achieve cluster linking, EMM uses three different language independent vector representations for each cluster. First vector contains the weighted list of references to countries mentioned in the articles, while the second vector contains the weighted list of mentioned people and organizations. The last vector contains the weighted list of Eurovoc subject domain descriptors. These descriptors are topics, such as \emph{air transport}, \emph{EC agreement}, \emph{competition} and \emph{pollution control} into which articles are automatically categorized~\shortcite{Pouliquen2006}. Similarity between clusters is then computed using a linear combination of the cosine similarities computed on the lists. If the similarity is above the threshold, the clusters are linked.

@@

In order to identify clusters $c_j$ that are equivalent to cluster $c_i$, we have developed a two-stage algoirhtm. For a cluster $c_i$, we first efficiently identify a small set of candidate clusters and then find those clusters among the candidates, which are equivalent to $c_i$. An example is  shown in  Figure~\ref{fig:clusters}.

The details of the first step are described in Algorithm~\ref{cluster_merge_algo1}. The algorithm begins by individually inspecting each article $a_i$ in the cluster $c_i$. Using a chosen method for computing cross-lingual document similarity (see Section~\ref{sec:models}), it identifies the 10 most similar articles to $a_i$ in each language $l \in L$. For each  similar article $a_j$, we identify its corresponding  cluster $c_j$ and add it to the set of candidates. The set of candidate clusters obtained in this way is several orders of magnitude smaller than the number of all clusters. Although computed document similarities are approximate, our  assumption  is that articles in different languages describing the same event, will generally have a higher similarity than articles about different events. While this assumption does not always hold, redundancy in the data mitigates these false positives. Since we compute the 10 most similar articles for each article in $c_i$, we are likely to identify all the relevant candidates for cluster $c_i$.

@@

\section{Discussion}

>>>>

\begin{abstract}
Today, we follow news  which is distributed globally and reported on in many different languages. When a significant event occurs, it is often reported on in many different sources. In this work, our goal is to consider the problem tracking events in a large multilingual stream. In this paper, we consider a particular aspect of this problem, namely how to link collections of articles in different languages which refer to the same event. Given a multi-lingual stream,  articles are first clustered according in each language we consider separately. Given these clusters, we first propose a
method to enables cross-lingual document similarity based on Wikipedia, which
 enables us to compute the similarity of any two articles regardless of language. Using this similarity, we then propose an approach to find and match clusters across languages which represent the same event. We provide an extensive evaluation of the system as a whole, as well as an evaluation of the quality of the similarity measure and linking algorithm.
 \begin{comment}
Main points:
\begin{itemize}
\item Problem of tracking events in a large multilingual stream - we reduce it to event linking
\item Two contributions. We propose a method that enables cross-lingaul document similarity an approach to linking multilingual data and an approach that uses is to link events.
\item Evaluation of cross-lingual approaches on Wikipedia and the event linking task.
\end{itemize}
\end{comment}
\end{abstract}
%\section{Overview}
%Structure
%\begin{itemize}
%\item Introduction
%\item Cross lingual document similarity (model)
%\item  Event Detection
%\item  Combing the approaches
%\item Experiments
%\item Conclusions
%\end{itemize}
%The story:
%\begin{itemize}
%\item Description of the problem - we would liek to understand events ans sequences of events, but our observables (e.g. news stories) occur in a variety of languages
%\item We present an approach to tackle this problem using a combination of techniques....
%\item Ultimately we present a tool showing the feasibility of our approach
%%\end{itemize}
%
%\section{Overview}
%Structure
%\begin{itemize}
%\item Introduction
%\item System overview
%\item Cross lingual document similarity (algorithms)
%\item Event linking
%\item Experiments
%\item Conclusions
%\end{itemize}
%The story:
%\begin{itemize}
%\item Description of the problem - we would like to understand global news as sequences of events, but our observables (e.g. news stories) occur in a variety of languages
%\item We present an approach to tackle this problem using a combination of techniques....
%\item Ultimately we present a tool showing the feasibility of our approach
%\end{itemize}
%

@@

The main application on which we test the above similiarity is cross-lingual event linking. In online media streams -- particularly new articles -- there is often duplication of reporting, different viewpoints or opinions, all centering around a single event. Same events are covered by many articles and the question we address is how to find all the articles in different languages that are describing a single event. We base our evaluation on an online system for detection of world events, Event Registry. We do not address the problem of detection of events in this paper but rather consider the problem that given a series of events, how may we best ``tag" or match articles in different languages to these events. The events are represented by clusters of articles and so ultimately our problem reduces to find suitable matchings between clusters with articles in different languages.

@@

The problem in the second phase of the pipeline is to identify the clusters describing the same events. Each article $a_i$ is written in a language $l$, where $\ell \in L = \{\ell_1,\ell_2,...,\ell_k\}$. For each language $\ell$, we generate and maintain a set of language-specific clusters $C_l$. That is, all articles are in language $l$. For any cluster $c_i \in C_{\ell_a}$, we would like to identify clusters $c_j \in C_{\ell_b}$ (where $\ell_a \neq \ell_b$) that describe the same event as $c_i$. We define \emph{equivalent clusters} as  pairs $(c_i,c_j)$ such that both clusters in the pair describe the same event in languages $C_{\ell_a}$ and $C_{\ell_b}$ respectively. Furthermore, we iterate over all the languages we consider. That is, given a cluster in language $\ell_i$, we look for matching clusters in language $\ell_j$ for $i\neq j$  in a pairwise fashion.

@@

Furthermore, the matching of clusters is a \emph{generalized matching}. We cannot assume that there is only one cluster per language per event, nor can we assume complete coverage - that there exists at least one cluster per event in every language. This implies that we cannot make any assumptions on the matching, e.g. one-to-one, complete, etc. This excludes the use of standard weighted bipartite matching type of algortihms for this problem. An example is shown in Figure~\ref{fig:clusters}, where a cluster may contain articles which are closely matched with many clusters in a different language.

We impose an additional requirement.  Identification of the equivalent clusters cannot be done exhaustively -- for a cluster $c_i$ we wish to avoid testing all other clusters for all the other languages. Performing exhaustive comparison for each cluster $c_i$ would result in $O(N^2)$ tests, where $N$ is the number of all clusters (over all languages), which is not feasible for when the number of clusters is on the order of tens of thousands.

@@

Although there are a number of services that aggregate news by identifying clusters of similar articles, there are very few service that provide linking of clusters over different languages. Google News as well as Yahoo! News are able to identify clusters of articles about same event, but they offer no linking of clusters across languages. The only service that provides cross-lingual cluster linking is the European Media Monitor (EMM)~\cite{Steinberger2008}. EMM clusters articles in 60 languages and then tries to determine which clusters of articles in different languages describe the same event. To achieve cluster linking, EMM uses three different language independent vector representations for each cluster. First vector contains the weighted list of references to countries mentioned in the articles, while the second vector contains the weighted list of mentioned people and organizations. The last vector contains the weighted list of Eurovoc subject domain descriptors. These descriptors are topics, such as \emph{air transport}, \emph{EC agreement}, \emph{competition} and \emph{pollution control} into which articles are automatically categorized~\shortcite{Pouliquen2006}. Similarity between clusters is then computed using a linear combination of the cosine similarities computed on the lists.

@@

In order to identify clusters $c_j$ that are equivalent to cluster $c_i$, we have developed a two-stage algoirhtm. First, for a cluster $c_i$, we efficiently identify a small set of candidate clusters and then  find the clusters from among the candidates which are equivalent to $c_i$. An example is  shown in  Figure~\ref{fig:clusters}.

The details of the first step are described in Algorithm~\ref{cluster_merge_algo1}. The algorithm begins by individually inspecting each article $a_i$ in the cluster $c_i$. Using CCA  (see Section~\ref{sec:CCA}),  it then identifies the 10 most similar articles to $a_i$ in each language $l \in L$. For each  similar article $a_j$, we identify its corresponding  cluster $c_j$ and add it to the set of candidates. \todo{we should say a few words why this is more efficient - since now we are comparing each article to all other articles - while we said it is not feadible for clusters}. While the CCA simliarity is approximate, our  assumption  is that articles in different languages describing the same event, will generally have a higher similarity than articles about different events. While this assumption does not always hold, redundancy in the data mitigates these false positives. Since we compute the 10 most similar articles for each article in $c_i$, we are likely to identify all the relevant candidates for cluster $c_i$.

@@

\section{Discussion and Future Work}

We now discuss some aspects of the methods and the system as a whole.
\begin{itemize}
\item \textbf{LSI and hub CCA} - We first comment on the empirical validation of LSI and hub CCA. On the task of mate retrieval we observe that refining the LSI based projections with hub CCA leads to improved retrieval precision, but the methods perform comparably on the task of event linking. Further inspection showed that the CCA based approach reached a higher precision on smaller clusters. The interpretation is that the linking features are highly aggregated for large clusters, which compensates the lower per-document percision of LSI. Another possible reason is, that the advantage that we show on Wikipedia is lost on the news domain - which indicates that domain adaptation should be explored.

\item \textbf{Features} - The experiments show that the hub CCA based features present good baseline, which can greatly benefit from additional semantic extraction based features. Even though the CCA based features do not greatly improve the system performance when the semantic features are used, there are two main benefits in the approach: the linking process can be sped up (smaller candidate cluster sets), and in the case when semantic extraction is not possible.

\item \textbf{Future work} - Currently the system is loosely coupled - the language component is built independently of the rest of the system, in particular the linking component. It is possible that better embeddings can be obtained by methods that jointly optimize a classification task and the embedding.

    Another point of interest is to evaluate the system on languages with scarce linguistic resources, where semantic annotation might not be available. For this reason, the labelled dataset of linked clusters should to be extended first. The mate retrieval evaluation showed that even for language pairs with no training set overlap, the hub cca recovers some signal.
